---
title: "FML assignment 3"
author: "HARI VINAYAK"
date: "2023-11-13"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#summary 


luster Interpretation:
Cluster Characteristics:
Cluster 1 ("Hold" Cluster): Firms like AGN, PHA, BAY have the highest PE_Ratio, but lower ROE.
Cluster 2 ("Moderate Buy/Hold" Cluster): JNJ, MRK, GSK, PFE have the highest Market_Cap and good Leverage.
Cluster 3 ("Buy or Sell" Cluster): AHM, AVE, WPI have lower Asset_Turnover and Beta.
Cluster 4 ("Buy" Cluster): IVX, MRX, ELN, CHTT have the lowest Market_Cap, but good Leverage and Beta.
Cluster 5 ("High Hold" Cluster): ABT, NVS, AZN, LLY, BMY, WYE, SGP have the lowest Revenue Growth but high Asset_Turnover and Net Profit Margin.


Cluster Recommendations:
Cluster 1: Hold these stocks.
Cluster 2: Moderate Buy or Hold.
Cluster 3: Consider buying or selling based on other factors.
Cluster 4: Buy these stocks.
Cluster 5: High Hold, especially for longer-term investments.


2. Pattern Analysis:
PE_Ratio (variable 10): Highest in Cluster 1, indicating a potential pattern for conservative investors.
Market_Cap (variable 1): Highest in Cluster 2, suggesting stability and attractiveness for moderate investors.
Asset_Turnover (variable 6): Lowest in Cluster 5, indicating a pattern for longer-term holding.


3. Naming Clusters:
Cluster 1: Conservative Hold
Cluster 2: Stable Holdings
Cluster 3: Variable Holdings
Cluster 4: Attractive Buys
Cluster 5: Long-Term Gems


```{r}
library(tidyverse)
```
```{r}
library(ggplot2) 
library(factoextra)
```
```{r}
library(ISLR) 
library(gridExtra)
```
```{r}
library(cluster) 
library(dplyr) 
library(tinytex)
PHARMACEUTICALS=read.csv("/Users/harivinayak/FML/pharma.csv")
```

# a Task 1
#Use only the numerical variables (1 to 9) to cluster the 21 firms. Justify the various choices made in conducting the cluster analysis, such as weights for different variables, the specific clustering algorithm(s) used, the number of clusters formed, and so on.
#Choosing the numerical variables and removing the Null Values from the dataset.
```{r}
colSums(is.na(PHARMACEUTICALS))
```
```{r}
pharma1 <- na.omit(PHARMACEUTICALS) 
#Provides the data after removing the incomplete cases.
pharma1
```
```{r}
row.names(pharma1)<- pharma1[,1]
pharma11<- pharma1[,3:11]
#Considering only numercial values i.e., 3-11 columns from csv file
head(pharma11)
```
```{r}
# Scaling and Normalisation the dataset(PARMACEUTICALS).
pharma12<-scale(pharma11)
head(pharma12)
```
```{r}
#To determine the number of clusters to do the cluster analysis using Elbow Method
fviz_nbclust(pharma12, kmeans, method = "wss")
```
```{r}
#By seeing the above graph from Elbow method, Graph is not clear to choose k=2 or 3 or 4 or 5
#Silhouette method for determining no of clusters
fviz_nbclust(pharma12, kmeans, method = "silhouette")
```
```{r}
#By seeing the graph from silhouette method, I can see sharp rise at k=5.
#So, considering the  silhouette method.
#Applying K-means
set.seed(64060)
k_5<- kmeans(pharma12,centers=5,nstart = 25)
#Visualizing the output
#centroids
k_5$centers
```
```{r}
fviz_cluster(k_5,data = pharma12) # to Visualize the clusters
```
```{r}
k_5
```
```{r}
 distance<- dist(pharma12, method = "euclidean")
fviz_dist(distance)
```
```{r}
## I can see there are 5 clusters and the center is defined after 25 restarts
#which is determined in kmeans.
#K-Means Cluster Analysis- Fit the data with 5 clusters
fit<-kmeans(pharma12,5)
#Finding the mean value of all quantitative variables for each cluster
aggregate(pharma12,by=list(fit$cluster),FUN=mean)
```

```{r}
pharma13<-data.frame(pharma12,fit$cluster)
pharma13
```
```{r}
head(pharma13)
```

```{r}
#To view the cluster plot
clusplot(pharma12,fit$cluster,color = TRUE,shade = TRUE,labels = 2,lines = 0)
```

```{r}
#Task 2 Interpret the clusters with respect to the numerical variables used in forming the clusters.
#By noticing the mean values of all quantitative variables for each cluster
#Cluster 1 - AGN, PHA, BAY - These have the highest PE_Ratio. ROE value is not good.
#Cluster 2 - JNJ, MRK, GSK, PFE - They have the highest market_Cap and has Good Leverage value.
#Cluster 3 - AHM, AVE, WPI - They have lowest asset_turnover,and lowest beta.
#Cluster 4 - IVX, MRX, ELN, CHTT - They have the lowest market capitalization, Leverage and Beta are good.
#Cluster 5 - ABT, NVS, AZN, LLY, BMY, WYE, SGP - They have lowest revenue growth, highest asset turnover.

#Task 3: Is there a pattern in the clusters with respect to the numerical variables (10 to 12)? (those are used in forming the clusters)
#For cluster 1: It  has the highest PE_Ratio and needs to be held as per the media recommendations.
#For cluster 2: It has the highest market_Cap and has Good Leverage value. And they can be moderately recommended.
#For cluster 3: It has lowest asset_turnover,and lowest beta. But media recommendations are highly positive.
#For cluster 4: The leverage ratio is high, they are moderately recommended.
#For Cluster 5: They have lowest revenue growth, highest assest turnover and highest net profit margin. 
#They are recommended to be held for longer time.

#Task 4: Provide an appropriate name for each cluster using any or all of the variables in the dataset.
#Cluster 1: Hold cluster -They have decent numbers.
#Cluster 2: Moderate Buy (or) Hold cluster.
#Cluster 3: Buy or Sell Cluster
#Cluster 4: Buy Cluster - It has good stability.
#Cluster 5: High Hold cluster
```


